---
title: "Penguin Analysis Using R"
author: "Margaret Lei"
date: 2026-09-28
execute:
  echo: true
  warning: false
---

## Analysis

First, let's load in the data about the Palmer Penguins; the first 6 rows are shown below.

```{r}
library(tidyverse)
library(palmerpenguins)
head(penguins)
```

\
How many islands do we have data for? Below, I count the unique names in the **island** column.

```{r}
#| message: false
n_islands <- n_distinct(penguins$island)

n_islands
```

\
Let's find the average flipper length by species. Below, I group the data by the values in the **species** column, and then calculate the average using the available flipper length measurements per species.

```{r}
#| label: avg_flip
#| fig-cap: "A table showing average flipper length in mm by species"

avg_flip <- penguins |> 
  group_by(species) |> 
  drop_na() |> 
  summarise(flipper_length_mm = mean(flipper_length_mm))
plot(avg_flip)
```

\
How about the average flipper length by species by island? I did the same thing as above, but this time also grouping by island.

```{r}
#| fig-cap: "A table showing average flipper length in mm by species by island"
avg_flip_per_island <- penguins |> 
  group_by(species, island) |> 
  drop_na() |> 
  summarise(flipper_length_mm = mean(flipper_length_mm))
avg_flip_per_island
```

\
It seems Adelie penguins on the island of Torgersen have slightly longer mean flipper length. Neat!

## Credits

Data source:\
Horst AM, Hill AP, Gorman KB (2020). palmerpenguins: Palmer Archipelago (Antarctica) penguin data. R package version 0.1.0. https://allisonhorst.github.io/palmerpenguins/. doi: 10.5281/zenodo.3960218.

Data available by [CC-0](https://creativecommons.org/share-your-work/public-domain/cc0/) licence.
